AbxD01 Analysis

### 2015-01-26 abxD01_analysis.Rmd
figure 5 updates

@@

@@

@@

Input files found on github:
1. abxD01.final.tx.2.subsample.2.pick.metro.relabund.d0s.txt

```{r, eval=FALSE}
#First calculating:
b<-read.delim("~/Desktop/mothur/abxD01/barcharts/abxD01.final.tx.2.subsample.2.pick.metro.relabund.d0s.txt", header=T)

avg1<-tapply(b$Otu001, b$order, mean)
sd1<-tapply(b$Otu001, b$order, sd)

avg11<-tapply(b$Otu011, b$order, mean)
sd11<-tapply(b$Otu011, b$order, sd)

avg02<-tapply(b$Otu002, b$order, mean)
sd02<-tapply(b$Otu002, b$order, sd)

avg03<-tapply(b$Otu003, b$order, mean)
sd03<-tapply(b$Otu003, b$order, sd)

avg7<-tapply(b$Otu007, b$order, mean)
sd7<-tapply(b$Otu007, b$order, sd)

avg05<-tapply(b$Otu005, b$order, mean)
sd05<-tapply(b$Otu005, b$order, sd)

avg16<-tapply(b$Otu016, b$order, mean)
sd16<-tapply(b$Otu016, b$order, sd)

avg06<-tapply(b$Otu006, b$order, mean)
sd06<-tapply(b$Otu006, b$order, sd)

avg04<-tapply(b$Otu004, b$order, mean)
sd04<-tapply(b$Otu004, b$order, sd)

@@

par(mar=c(2, 4, 2, 3) +0.1)
plot1<-barplot(avg1, col="darkblue", cex.axis=1.3, xaxt="n") 
error.bar(plot1, avg1, sd1) #plot SD

>>>>

### Figure 3: Barchart

@@

### Figure 3: Statistics

```{r, eval=FALSE}
file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allstreptitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrStrep",]
kruskal.test(file$Otu001 ~ file$expgroup)
kruskal.test(file$Otu003 ~ file$expgroup)
kruskal.test(file$Otu002 ~ file$expgroup)
kruskal.test(file$Otu005 ~ file$expgroup)
kruskal.test(file$Otu004 ~ file$expgroup)
kruskal.test(file$Otu014 ~ file$expgroup)
kruskal.test(file$Otu006 ~ file$expgroup)
kruskal.test(file$Otu007 ~ file$expgroup)
kruskal.test(file$Otu009 ~ file$expgroup)
kruskal.test(file$Otu015 ~ file$expgroup)
kruskal.test(file$Otu017 ~ file$expgroup)
kruskal.test(file$Other ~ file$expgroup)

test <- pairwise.wilcox.test(file$Otu001, file$expgroup, p.adj="BH")
comparisons <- length(test$p.value[]) - sum(is.na(test$p.value))

pairwise.wilcox.test(file$Otu003, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu005, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu002, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu004, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu014, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu006, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu007, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu009, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu015, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu017, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Other, file$expgroup, p.adj="BH")

file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allvanctitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrVanc",]
kruskal.test(file$Otu001 ~ file$expgroup)
kruskal.test(file$Otu002 ~ file$expgroup)
kruskal.test(file$Otu003 ~ file$expgroup)
kruskal.test(file$Otu005 ~ file$expgroup)
kruskal.test(file$Otu004 ~ file$expgroup)
kruskal.test(file$Otu014 ~ file$expgroup)
kruskal.test(file$Otu006 ~ file$expgroup)
kruskal.test(file$Otu007 ~ file$expgroup)
kruskal.test(file$Otu008 ~ file$expgroup)
kruskal.test(file$Otu019 ~ file$expgroup)
kruskal.test(file$Otu018 ~ file$expgroup)
kruskal.test(file$Otu017 ~ file$expgroup)
kruskal.test(file$Other ~ file$expgroup)

pairwise.wilcox.test(file$Otu001, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu003, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu005, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu002, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu004, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu014, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu006, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu007, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu008, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu019, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu018, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu017, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Other, file$expgroup, p.adj="BH")

file<-read.csv("~/Documents/Github/abxD01/Figure 3/abxD01.final.tx.2.subsample.allceftitr.forlogscale.csv", header=T)
file<-file[file$expgroup!="1untrCef",]
kruskal.test(file$Otu001 ~ file$expgroup)
kruskal.test(file$Otu002 ~ file$expgroup)
kruskal.test(file$Otu003 ~ file$expgroup)
kruskal.test(file$Otu005 ~ file$expgroup)
kruskal.test(file$Otu004 ~ file$expgroup)
kruskal.test(file$Otu014 ~ file$expgroup)
kruskal.test(file$Otu006 ~ file$expgroup)
kruskal.test(file$Otu007 ~ file$expgroup)
kruskal.test(file$Otu008 ~ file$expgroup)
kruskal.test(file$Otu009 ~ file$expgroup)
kruskal.test(file$Otu019 ~ file$expgroup)
kruskal.test(file$Otu018 ~ file$expgroup)
kruskal.test(file$Otu016 ~ file$expgroup)
kruskal.test(file$Otu024 ~ file$expgroup)
kruskal.test(file$Otu011 ~ file$expgroup)
kruskal.test(file$Other ~ file$expgroup)

pairwise.wilcox.test(file$Otu001, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu003, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu005, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu002, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu004, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu014, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu006, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu007, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu008, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu009, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu011, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu019, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu018, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu016, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Otu024, file$expgroup, p.adj="BH")
pairwise.wilcox.test(file$Other, file$expgroup, p.adj="BH")

@@

### Figure 5: Random Forest Analysis

Performed RF analysis on family level phylotypes:
```{r, eval=FALSE}
topdose_tx2<-read.csv("~/Documents/Github/abxD01/Figure 5/abxD01.final.tx.2.subsample.2.shared.rf.topdose.regression.logtrans.csv", header=T)
topdose_tx2<-topdose_tx2[,-1]

#fit the randomforest model
model_tx2 <- randomForest(nextDayCFU~., 
                      data = topdose_tx2,  outscale=TRUE,
                      importance=TRUE, proximity=TRUE,
                      keep.forest=TRUE, ntree=5000
)
plot(model_tx2)

print(model_tx2)

#what are the important variables (via permutation) #type 1 is mean decrease in accuracy, type 2 is mean decrease in node impurity
par(mfrow=c(1, 1)) 
varImpPlot(model_tx2, type=1)
imp<-importance(model_tx2)
most.imp<-rownames(imp[order(imp[, "%IncMSE"], decreasing=T)[1:17],])
```

### Figure 5: Barchart

@@

Input files found on github:
1. abxD01.final.tx.2.subsample.2.metro.relabund.D0s.csv

```{r, eval=FALSE}
#First calculating:
metroD0<-read.csv("~/Documents/Github/abxD01/Figure 5/abxD01.final.tx.2.subsample.2.metro.relabund.D0s.csv", header=T)

avg01<-tapply(metroD0$Otu001, metroD0$order, mean)
sd01<-tapply(metroD0$Otu001, metroD0$order, sd)

avg14<-tapply(metroD0$Otu014, metroD0$order, mean)
sd14<-tapply(metroD0$Otu014, metroD0$order, sd)

avg7<-tapply(metroD0$Otu007, metroD0$order, mean)
sd7<-tapply(metroD0$Otu007, metroD0$order, sd)

avg09<-tapply(metroD0$Otu009, metroD0$order, mean)
sd09<-tapply(metroD0$Otu009, metroD0$order, sd)

avg02<-tapply(metroD0$Otu002, metroD0$order, mean)
sd02<-tapply(metroD0$Otu002, metroD0$order, sd)

avg13<-tapply(metroD0$Otu013, metroD0$order, mean)
sd13<-tapply(metroD0$Otu013, metroD0$order, sd)

avg03<-tapply(metroD0$Otu003, metroD0$order, mean)
sd03<-tapply(metroD0$Otu003, metroD0$order, sd)

avg05<-tapply(metroD0$Otu005, metroD0$order, mean)
sd05<-tapply(metroD0$Otu005, metroD0$order, sd)

avg08<-tapply(metroD0$Otu008, metroD0$order, mean)
sd08<-tapply(metroD0$Otu008, metroD0$order, sd)

avg06<-tapply(metroD0$Otu006, metroD0$order, mean)
sd06<-tapply(metroD0$Otu006, metroD0$order, sd)

avg04<-tapply(metroD0$Otu004, metroD0$order, mean)
sd04<-tapply(metroD0$Otu004, metroD0$order, sd)

avg12<-tapply(metroD0$Otu012, metroD0$order, mean)
sd12<-tapply(metroD0$Otu012, metroD0$order, sd)

# avg11<-tapply(metroD0$Otu011, metroD0$order, mean)
# sd11<-tapply(metroD0$Otu011, metroD0$order, sd)
# 
# avg05<-tapply(metroD0$Otu005, metroD0$order, mean)
# sd05<-tapply(metroD0$Otu005, metroD0$order, sd)
# 
# avg16<-tapply(metroD0$Otu016, metroD0$order, mean)
# sd16<-tapply(metroD0$Otu016, metroD0$order, sd)

@@

par(mar=c(2, 4, 2, 3) +0.1)
plot01<-barplot(avg01, col="darkblue", cex.axis=1.3, xaxt="n") 
error.bar(plot01, avg01, sd01) #plot SD
